Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd
Finish findings

The results of the method are summarised in Figure \@ref(fig:res) and Table 2.

```{r res, fig.cap="Results, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled."}
tmap_mode("view")
tm_shape(r_pct_no_overlap) + tm_lines(col = "lightblue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top) + tm_lines(col = "blue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top_n) + tm_text("name")
```

@@

>>>>

The results of the method are summarised in Figure \@ref(fig:res) and Table 2.
We have found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing the 85,000 road segments for Leeds down to candidate segments with more than 1 lane near key destinations that can be visualised in an interactive map can has great potential to support policy-makers, especially when decisions need to be made fast.

```{r res, fig.cap="Results, showing road segments with a spare lane (light blue) and road groups with a minium threshold length, 1km in this case (dark blue). The top 10 road groups are labelled."}
tmap_mode("view")
tm_shape(r_pct_no_overlap) + tm_lines(col = "lightblue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top) + tm_lines(col = "blue", lwd = 4, alpha = 0.6) +
  tm_shape(r_pct_top_n) + tm_text("name") +
  tm_shape(h_leeds) + tm_dots(size = 0.1)
```

@@

The approach is not without limitations.
Its reliance on data rather than community engagement represents a rather top-down approach to transport planning.
To overcome this issue future work could seek to incorporate the results such as those presented above into a participatory map of the type shown in Figure 1.
A major advantage of the approach is that it is scalable.
It would be feasible to run the method for every city in the UK for which there is data, given sufficient computer and developer resource.
Given the recent interest in and funding for pop-up cycleways, rolling-out the method quickly, while being agile to adapt the method and parameters for different cities, could help ensure that funding for pop-up infrastructure is spent in an evidence-based way.
